---
title: "bank loan dummies"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(janitor)
library(tidyverse)
library(readxl)

loan_data <- readRDS("ppp_covidadj.rds")
old_data <- readRDS("ppp_loanonly_all_loans.rds")
```


```{r}
# Don't run this anymore
banks <- old_data %>%
  select(lender) %>%
  group_by(lender) %>%
  summarize(number_of_loans = n(), .groups = "drop") %>%
  ungroup() %>%
  mutate(lender = tolower(lender))

banks_gov_project <- loan_data %>%
  select(lender) %>%
  group_by(lender) %>%
  summarize(number_of_loans = n(), .groups = "drop") %>%
  filter(number_of_loans >= 1000)
```


```{r}
bank_ppp_policy_manual <- read_excel('raw_data/bank_ppp_policy_manual.xlsx', sheet = "Sheet2") %>%
  mutate(sba_name = tolower(sba_name)) %>%
  mutate(sba_name = str_trim(sba_name, side = "both")) %>%
  drop_na(preference, requirement)

ppp_setup <- loan_data %>%
  mutate(lender = str_trim(lender, side = "both"), lender = tolower(lender))

ppp_allvars_1019_banking <- left_join(ppp_setup, bank_ppp_policy_manual,
                                      by = c("lender" = "sba_name")) %>%
  mutate(requirement = ifelse(str_detect(lender, pattern = "\\sfcu$"), 1, requirement),
         requirement = ifelse(str_detect(lender, pattern = "\\scu$"), 1, requirement),
         requirement = ifelse(str_detect(lender, pattern = "credit union"), 1, requirement)) %>%
  drop_na(requirement) %>%
  mutate(preference = replace_na(preference, 0))
```


```{r}
# Should I exclude credit unions? I'm matching credit unions and making them members only
bank_loan_policies <- banks %>%
  mutate(members_only = ifelse(str_detect(lender, pattern = "\\sfcu$"), 1, 0),
         members_only = ifelse(str_detect(lender, pattern = "\\scu$"), 1, members_only),
         members_only = ifelse(str_detect(lender, pattern = "credit union"), 1, members_only))


```


```{r}
# Counting the number of loans per bank
loan_numbers <- old_data %>%
  select(lender) %>%
  group_by(lender) %>%
  summarize(bank_ppp_issued = n(), .groups = "drop") %>%
  mutate(lender = tolower(lender))

ppp_allvars_1024 <- left_join(ppp_allvars_1019_banking, loan_numbers, by = "lender") %>%
  rename("cook_pvi" = "pct", 
         "black_percent" = "percent_estimate_race_total_population_one_race_black_or_african_american",
         "white_percent" = "percent_estimate_race_total_population_one_race_white",
         "median_family_income" = "estimate_median_income_dollars_families_families",
         "population" = "estimate_total") %>%
  select(-loan_range)
```


```{r}
# Rural data dummy coding
rural <- read_excel("raw_data/crosswalks/forhp-eligible-zips.xlsx") %>%
  clean_names() %>%
  select(-state) %>%
  mutate(rural = 1)

ppp_allvars_1024_rural <- left_join(ppp_allvars_1024, rural, by = "zip") %>%
  mutate(rural = replace_na(rural, 0)) %>%
  mutate(rural = as.double(rural))
```


```{r}
# Business counts coding
biz_count <- read_csv("raw_data/acs_business/ZBP2014.CB1400ZBP_data_with_overlays_2020-10-19T095307.csv",
                      skip = 1) %>%
  clean_names()  %>%
  mutate(geographic_area_name = substring(geographic_area_name, 5, 9)) %>%
  mutate(geographic_area_name = str_trim(geographic_area_name, side = "both")) %>%
  filter(meaning_of_2012_naics_code == "Total for all sectors") %>%
  select(geographic_area_name, number_of_establishments)

ppp_allvars_1024 <- left_join(ppp_allvars_1024_rural, biz_count, 
                              by = c("zip" = "geographic_area_name")) %>%
  #rename("white_percent" = "White_percent") %>%
  drop_na(number_of_establishments, white_percent, black_percent,
          high_school_pct, banks_per_pop, cook_pvi, mean_start_cases_weighted,
          mean_start_deaths_weighted, bank_ppp_issued, rural)
```


```{r}
# bank_deposits <- read_csv("raw_data/fdic/All_Reports_20200630_Total_Deposits.csv") %>%
#   select(name, dep) %>%
#   mutate(dep = as.double(dep), name = tolower(name))
```


```{r}
# left_join(banks, bank_deposits, by = c("lender" = "name")) %>%
#   group_by(lender) %>%
#   filter(is.na(dep))
```


```{r}
ppp_logtest <- ppp_allvars_1019 %>%
  mutate(logdays = ifelse(log(days_to_approval) == -Inf, 0, log(days_to_approval)))
```


```{r}
# Deprecated code now
ppp_allvars_1019_marital <- readRDS('ppp_allvars_1019_marital.rds') %>%
  # Population weight the businesses -- I forgot to do this the first time
  mutate(businesses_per_pop = number_of_establishments / (population/10000)) %>%
  select(-number_of_establishments)
```


```{r}
ppp_allvars_1024 <- ppp_allvars_1024  %>%
  # Population weight the businesses -- I forgot to do this the first time
  mutate(businesses_per_pop = number_of_establishments / (population/10000)) %>%
  select(-number_of_establishments)

test_regression <-
  lm(ppp_allvars_1019_banking$days_to_approval ~ 1 + ppp_allvars_1019_banking$median_family_income +
       ppp_allvars_1019_banking$black_percent +
       ppp_allvars_1019_banking$white_percent + ppp_allvars_1019_banking$high_school_pct +
       ppp_allvars_1019_banking$banks_per_pop + 
       ppp_allvars_1019_banking$loan_350_1mil + ppp_allvars_1019_banking$loan_150_350 + 
       ppp_allvars_1019_banking$loan_5mil_10mil +
       ppp_allvars_1019_banking$loan_2mil_5mil + ppp_allvars_1019_banking$loan_1mil_2mil +
       ppp_allvars_1019_banking$cook_pvi + ppp_allvars_1019_banking$mean_start_cases_weighted + 
       ppp_allvars_1019_banking$mean_start_deaths_weighted + ppp_allvars_1019_banking$bank_ppp_issued +
       ppp_allvars_1019_banking$rural + ppp_allvars_1019_banking$businesses_per_pop +
       ppp_allvars_1019_banking$married_percent + ppp_allvars_1019_banking$preference +
       ppp_allvars_1019_banking$requirement)

summary(test_regression)
```


```{r}
ppp_logtest <- ppp_allvars_1019_banking %>%
  mutate(logdays = ifelse(log(days_to_approval) == -Inf, 0, log(days_to_approval))) %>%
  mutate(logbiz = ifelse(log(businesses_per_pop) == -Inf, 0, log(businesses_per_pop))) %>%
  mutate(logbanks = ifelse(log(banks_per_pop) == -Inf, 0, log(banks_per_pop)))

log_regression_test <- 
    lm(ppp_logtest$logdays ~ 1 + ppp_logtest$median_family_income +
       ppp_logtest$black_percent +
       ppp_logtest$white_percent + ppp_logtest$high_school_pct +
       ppp_logtest$logbanks + 
       ppp_logtest$loan_350_1mil + ppp_logtest$loan_150_350 + 
       ppp_logtest$loan_5mil_10mil +
       ppp_logtest$loan_2mil_5mil + ppp_logtest$loan_1mil_2mil +
       ppp_logtest$cook_pvi + ppp_logtest$mean_start_cases_weighted + 
       ppp_logtest$mean_start_deaths_weighted + ppp_logtest$bank_ppp_issued +
       ppp_logtest$rural + ppp_logtest$logbiz + 
    ppp_logtest$married_percent + ppp_logtest$preference + 
      ppp_logtest$preference * ppp_logtest$black_percent + 
      ppp_logtest$requirement * ppp_logtest$black_percent +
    ppp_logtest$requirement)

summary(log_regression_test)
```

```{r}
# Adding in marital status
marital <- read_csv("raw_data/acs_marital/ACSST5Y2018.S1201_data_with_overlays_2020-10-19T152147.csv",
                    skip = 1) %>%
  clean_names() %>%
  select(geographic_area_name, estimate_now_married_except_separated_population_15_years_and_over) %>%
  mutate(geographic_area_name = map_chr(geographic_area_name, ~ substring(., 6)),
         geographic_area_name = str_trim(geographic_area_name, side = "both")) %>%
  rename("married_percent" = "estimate_now_married_except_separated_population_15_years_and_over")

ppp_allvars_1024_marital <- left_join(ppp_allvars_1024, marital, 
                                      by = c("zip" = "geographic_area_name")) %>%
  drop_na(married_percent) %>%
  mutate(married_percent = as.double(married_percent))